---
title: "Scientific report - "
author: ""
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
```

```{r include=FALSE}
# updated May 2, 2021
cobap <- rio::import(here::here("data", "policy_list.csv")) %>%   select(ISO3, COUNTRY_NAME, POLICY_TYPE, POLICY_SUBTYPE, START_DATE, END_DATE)

control_data <- readRDS("coviddata.RDS") # control Vars

data <- left_join(cobap, control_data ) %>% 
  drop_na() 

#convert some columns to correct types
data[, 9:ncol(data)] <- lapply(9:ncol(data), function(x) 
                               as.numeric(data[[x]]))
data[, 3:4] <- lapply(3:4, function(x) 
                               as.factor(data[[x]]))

# date variables

data <- data %>% 
  mutate(START_DATE = lubridate::mdy(data$START_DATE), 
         END_DATE = lubridate::mdy(data$END_DATE))
```

### Replication of Liang's et al.
 
"In the multiple regression analysis, Covid-19 mortality rate was regressed on Covid-19 test number, case number, critical case rate, government effectiveness score, proportion of population aged 65 or older, number of beds, deaths attributable to communicable diseases, and transport infrastructure quality score." (Liang, et al, p.2)

```{r replication}
# multiple regression
model1 <- lm(mortalityrate ~ `tests/100` + `cases/1000` + `critical case rate` +
               `Score` + `population_65_percent` + beds + `death_communicable_disease`+
               logisics_score,
               data = data)
summary(model1)
```
### Adding POLICY_TYPE in COBAP data

A multiple linear regression was run to examine the relationship between mortality rate and border closure policy type after controlling for Covid-19 test number, case number, critical case rate, government effectiveness score, proportion of the population aged 65 or older, number of beds, deaths attributable to communicable diseases, and transport infrastructure quality score. Changing POLICY_TYPE from COMPLETE to PARTIAl significantly lower the mortality rate by 0.087 (sd = 0.04), t(567) = -2.1, p = 0.03. 

```{r adding cobap}
# POLICY_TYPE 
model_policytype <- lm(mortalityrate ~ POLICY_TYPE + `tests/100` + `cases/1000` + `critical case rate` +
               `Score` + `population_65_percent` + beds + `death_communicable_disease`+
               logisics_score,
               data = data)

summary(model_policytype)
```

```{r include=FALSE}
# date
model_policytype <- lm(mortalityrate ~ POLICY_TYPE + `tests/100` + `cases/1000` + `critical case rate` +
               `Score` + `population_65_percent` + beds + `death_communicable_disease`+
               logisics_score,
               data = data)
head(data)
# during the week 2020-03-15 ~ 2020-03-21 , 144 policies were issued 
peaktime <- data %>% 
  add_count(week = lubridate::floor_date(START_DATE, "week")) %>% 
  filter(week == "2020-03-15")

model_policytype_peaktime <- lm(mortalityrate ~ POLICY_TYPE + `tests/100` + `cases/1000` + `critical case rate` +
               `Score` + `population_65_percent` + beds + `death_communicable_disease`+
               logisics_score,
               data = peaktime)
summary(model_policytype_peaktime)
```
### During the weeks of more than 50 policies issued

When considering only weeks in which more than 50 policies were issued per week worldwide, the above effect of POLICY_TYPE changed its direction, but was no longer significant. b1 = 0.01, sd = 0.07, t(198) = 0.16, p = 0.87. 

```{r}
# during the weeks that had more than 50 policies issued/ week -> 214 policies
  week_morethan50 <- data %>% 
  add_count(week = lubridate::floor_date(START_DATE, "week")) %>% 
  arrange(desc(n)) %>% 
  filter(n > 50)

model_policytype_week_morethan50 <- lm(mortalityrate ~ POLICY_TYPE + `tests/100` + `cases/1000` + `critical case rate` + `Score` + `population_65_percent` + beds + `death_communicable_disease`+
               logisics_score,
               data = week_morethan50)
summary(model_policytype_week_morethan50)
```

